### 2022-05-11 manuscript.Rmd
Add jackknife analysis

```{r, setup, include=FALSE}
# Load packages
library(papaja)
library(here)
library(readxl)
library(scales)
library(tidyverse)
library(magrittr)
library(metafor)
library(brms)
library(bayestestR)
library(tidybayes)
library(cowplot)

@@

# Re-run steps that take a long time?
run <- list(
  bayesian_models = FALSE,
  sensitivity_analysis = FALSE
)

>>>>

```{r, setup, include=FALSE}
# Load packages
library(papaja)
library(here)
library(readxl)
library(scales)
library(tidyverse)
library(magrittr)
library(furrr)
library(metafor)
library(brms)
library(bayestestR)
library(tidybayes)
library(cowplot)

@@

# Re-run steps that take a long time?
run <- list(
  bayesian_models = FALSE,
  jackknife_analysis = FALSE,
  sensitivity_analysis = FALSE
)

### 2022-05-11 supplement.Rmd
Add jackknife analysis

@@

```{r, tabs5, include=TRUE}
# Helper functions for printing results as a table
print_res_table <- function(res, label_1, label_2) {
  spread_draws(res, `b_.*`, `sd_.*`, regex = TRUE, ndraws = NULL) %>%
    transmute(
      `Hedges' $g$` = b_Intercept,
      `$\\sigma_\\text{article}^2$` = sd_article__Intercept^2,
      `$\\sigma_\\text{experiment}^2$` = `sd_article:experiment__Intercept`^2,
      `${ICC}$` = `$\\sigma_\\text{article}^2$` /
        (`$\\sigma_\\text{article}^2$` + `$\\sigma_\\text{experiment}^2$`)
    ) %>%
    summarize(across(.fns = mean_qi)) %>%
    map_dfc(~ print_ci(.$ymin, .$ymax, mean = .$y)) %>%
    bind_cols(Manipulation = label_1, ` ` = label_2, .)
}

# Combine results for the (main) meta-analysis of mental rotation performance
tab_sens <- res_sens %>%
  select(res, manipulation_name, manipulation_value) %>%
  pmap_dfr(function(res, manipulation_name, manipulation_value) {
    print_res_table(res, manipulation_name, manipulation_value)
  })

@@

```{r, tabs6, include=TRUE}
# Helper functions for printing results as a table
print_res_reg_table <- function(res_reg, label_1, label_2) {
  spread_draws(res_reg, `b_.*`, `sd_.*`, regex = TRUE, ndraws = NULL) %>%
    transmute(
      `Intercept` = b_Intercept,
      `Female - mixed` = b_gender2M1,
      `Male - female` = b_gender3M2,
      `Age (per year)` = b_age_c,
      `Habituation - VoE` = b_task2M1,
      `[Female - mixed] $\\times$ age` = `b_gender2M1:age_c`,
      `[Male - female] $\\times$ age` = `b_gender3M2:age_c`
    ) %>%
    summarize(across(.fns = mean_qi)) %>%
    map_dfc(~ print_ci(.$ymin, .$ymax, mean = .$y)) %>%
    bind_cols(Manipulation = label_1, ` ` = label_2, .)
}

# Combine results for the meta-regression of mental rotation performance
tab_sens_reg <- res_sens %>%
  select(res_reg, manipulation_name, manipulation_value) %>%
  pmap_dfr(function(res_reg, manipulation_name, manipulation_value) {
    print_res_reg_table(res_reg, manipulation_name, manipulation_value)
  })

@@

```{r, tabs7, include=TRUE}
# Combine results for the meta-analysis of gender differences
tab_sens_gender <- res_sens %>%
  filter(!map_lgl(res_gender, is.null)) %>%
  select(res_gender, manipulation_name, manipulation_value) %>%
  pmap_dfr(function(res_gender, manipulation_name, manipulation_value) {
    print_res_table(res_gender, manipulation_name, manipulation_value)
  })

>>>>

```{r, jackknife, include=TRUE}
# Helper functions for printing results from Bayesian model as a table
print_res_table <- function(res,
                            label_1 = NULL,
                            label_2 = NULL,
                            label_col_1 = "label_1",
                            label_col_2 = "label_2") {
  spread_draws(res, `b_.*`, `sd_.*`, regex = TRUE, ndraws = NULL) %>%
    transmute(
      `Hedges' $g$` = b_Intercept,
      `$\\sigma_\\text{article}^2$` = sd_article__Intercept^2,
      `$\\sigma_\\text{experiment}^2$` = `sd_article:experiment__Intercept`^2,
      `${ICC}$` = `$\\sigma_\\text{article}^2$` /
        (`$\\sigma_\\text{article}^2$` + `$\\sigma_\\text{experiment}^2$`)
    ) %>%
    summarize(across(.fns = mean_qi)) %>%
    map_dfc(~ print_ci(.$ymin, .$ymax, mean = .$y)) -> tab
  if (!is.null(label_2)) {
    label_2_tab <- tibble(tmp = c(label_2, rep(NA, nrow(tab) - 1))) %>%
      rename(!!label_col_2 := tmp)
    tab <- cbind(label_2_tab, tab)
  }
  if (!is.null(label_1)) {
    label_1_tab <- tibble(tmp = c(label_1, rep(NA, nrow(tab) - 1))) %>%
      rename(!!label_col_1 := tmp)
    tab <- cbind(label_1_tab, tab)
  }
  return(tab)
}

# Re-run the jackknife analysis only if requested
jackknife_file <- here(tables_dir, "jackknife.csv")
if (run$jackknife_analysis) {

  # Re-fit the meta-analysis, leaving one experiment out at a time
  # Using parallelization with `furrr`
  n_cores <- availableCores()
  n_workers <- n_cores %/% n_chains
  plan(multisession, workers = n_workers)
  future_map_dfr(seq_len(nrow(dat[1:2, ])), function(jackknife_index) {
    dat_jackknife <- dat[-jackknife_index, ]
    res_jackknife <- update(res_brm, newdata = dat_jackknife, refresh = 0)
    print_res_table(
      res_jackknife,
      label_1 = dat$article[jackknife_index],
      label_2 = dat$group_long[jackknife_index],
      label_col_1 = "Article", label_col_2 = "Experiment"
    )
  }) -> jackknife_tab

  # Save the table
  write_csv(jackknife_tab, file = jackknife_file)
} else {

  # Otherwise we load the pre-computed results
  jackknife_tab <- read_csv(jackknife_file, col_types = "c")
}

# Display the table
apa_table(
  jackknife_tab,
  align = "llcccc",
  caption = "Jackknife (leave-one-out) analysis",
  font_size = "scriptsize",
  escape = FALSE
)
```

@@

```{r, tabs5, include=TRUE}
# Combine results for the (main) meta-analysis of mental rotation performance
tab_sens <- res_sens %>%
  select(res, manipulation_name, manipulation_value) %>%
  pmap_dfr(function(res, manipulation_name, manipulation_value) {
    print_res_table(
      res,
      label_1 = manipulation_name, label_2 = manipulation_value,
      label_col_1 = "Manipulation", label_col_2 = " "
    )
  })

@@

```{r, tabs6, include=TRUE}
# Helper functions for printing results as a table
print_res_reg_table <- function(res_reg,
                                label_1,
                                label_2,
                                label_col_1,
                                label_col_2) {
  spread_draws(res_reg, `b_.*`, `sd_.*`, regex = TRUE, ndraws = NULL) %>%
    transmute(
      `Intercept` = b_Intercept,
      `Female - mixed` = b_gender2M1,
      `Male - female` = b_gender3M2,
      `Age (per year)` = b_age_c,
      `Habituation - VoE` = b_task2M1,
      `[Female - mixed] $\\times$ age` = `b_gender2M1:age_c`,
      `[Male - female] $\\times$ age` = `b_gender3M2:age_c`
    ) %>%
    summarize(across(.fns = mean_qi)) %>%
    map_dfc(~ print_ci(.$ymin, .$ymax, mean = .$y)) -> tab
  if (!is.null(label_2)) {
    label_2_tab <- tibble(tmp = c(label_2, rep(NA, nrow(tab) - 1))) %>%
      rename(!!label_col_2 := tmp)
    tab <- cbind(label_2_tab, tab)
  }
  if (!is.null(label_1)) {
    label_1_tab <- tibble(tmp = c(label_1, rep(NA, nrow(tab) - 1))) %>%
      rename(!!label_col_1 := tmp)
    tab <- cbind(label_1_tab, tab)
  }
  return(tab)
}

# Combine results for the meta-regression of mental rotation performance
tab_sens_reg <- res_sens %>%
  select(
    res_reg, manipulation_name, manipulation_value
  ) %>%
  pmap_dfr(function(res_reg, manipulation_name, manipulation_value) {
    print_res_reg_table(
      res_reg,
      label_1 = manipulation_name, label_2 = manipulation_value,
      label_col_1 = "Manipulation", label_col_2 = " "
    )
  })

@@

```{r, tabs7, include=TRUE}
# Combine results for the meta-analysis of gender differences
tab_sens_gender <- res_sens %>%
  filter(!map_lgl(res_gender, is.null)) %>%
  select(res_gender, manipulation_name, manipulation_value) %>%
  pmap_dfr(function(res_gender, manipulation_name, manipulation_value) {
    print_res_table(
      res_gender,
      label_1 = manipulation_name, label_2 = manipulation_value,
      label_col_1 = "Manipulation", label_col_2 = " "
    )
  })
